---
title: "Homework 6"
author: "Bingkun Luo"
date: "11/22/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
library(faraway)
library(modelr)

```

#### Problem 1
##### a

```{r}
birth_weight = read_csv("./data/birthweight.csv")%>%
                mutate(babysex = as.factor(babysex),
                       frace = as.factor(frace),
                       malform = as.factor(malform),
                       mrace = as.factor(mrace))

str(birth_weight)
```

Loaded and checked there is `r sum(is.na(birth_weight))` NAs in the imported dataset for the regression analysis.

##### b
Backward elimination example using step, 
Fristly remove the entire categorical variable, since it doesnot make much sense if the model selection only retain some of the  multiple levels.
```{r}
mod = lm(bwt~.-babysex-frace-mrace,data = birth_weight)
back = step(mod,direction = c("backward")) 
summary(back)
```


The model I selected by Backward selection based on AIC is 

```{r}
fit = lm(bwt~bhead+blength+delwt+fincome+gaweeks+menarche+mheight+momage+parity+ppwt+smoken,data = birth_weight)
fit
summary(fit)
```



Plot:

```{r}

plot = as_tibble(add_residuals(fit,data=add_predictions(fit,data=birth_weight)))
ggplot(plot, aes(x=pred,y=resid))+
  geom_point(alpha = 0.4)
  

```



Other two models:

```{r}
fit_1 = lm(bwt~blength+gaweeks,data = birth_weight)
fit_2 = lm(bwt~bhead*blength*babysex,data = birth_weight)

```

Cross validation:

```{r}

set.seed(1)
cv_df = 
  crossv_mc(birth_weight,100) 
cv_df =
  cv_df %>% 
  mutate(train = map(train, as_tibble),
         test = map(test, as_tibble))
```


```{r}
cv_df = 
  cv_df %>% 
  mutate(fit = map(train,~lm(bwt~bhead+blength 
        +delwt+fincome+gaweeks+menarche+mheight+momage+parity+ppwt+smoken,data = .)),
        fit_1 = map(train,~lm(bwt~blength+gaweeks,data = .)),
        fit_2 = map(train,~lm(bwt~bhead*blength*babysex,data = .))) %>% 
  mutate(rmse_fit = map2_dbl(fit, test, ~rmse(model = .x, data = .y)),
         rmse_fit_1 = map2_dbl(fit_1, test, ~rmse(model = .x, data = .y)),
         rmse_fit_2 = map2_dbl(fit_2, test, ~rmse(model = .x, data = .y)))
```



```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model))%>%
  group_by(model)%>%
  summarise(mean_rmse = mean(rmse))%>%
  pivot_wider(names_from = model,values_from = mean_rmse)%>%
  kableExtra::kable(type = "markdown")
```

#### Problem 2
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

##### a

Simple linear regression

```{r}
boot_straps = weather_df %>% 
              modelr::bootstrap(n = 5000)%>%
              mutate(
                fitted =map(strap,~lm(tmax~tmin,data = .x)),
                results1 = map(fitted,broom::tidy),
                results2 = map(fitted,broom::glance))%>%
              select(-strap, -fitted)
  
              
  




lm(tmax~tmin,data = weather_df)%>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)

lm(tmax~tmin,data = weather_df)%>% 
  broom::glance()%>%
  knitr::kable(digits = 3)
```












